---
title: "National Meteorological Service Dataset"
author: "Konstantinos Vantas"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

With this vignette the raw data that have been downloaded from www.emy.gr are transformed from a list of csv files to a tidy data frame, using the function `emy_create`.
```{r emy_data_create}
# the data from emy are downloaded to the folder ./raw-data/emy the following
# command will create a list of directories created in that folder
dir_names <- list.files('./emy', full.names = TRUE)

# these directories have the raw data from every station
dir_names
```

The following code will create a data frame with the available meteorological data. 

```{r emy_data_frame}
source(file = "./emy_create.R")
emy_data <- emy_create(dir_names)
```

The variables in the created data frame are:
```{r emy_df_names}
names(emy_data)
```

and some basic statistic values:
```{r emy_stats}
summary(emy_data)
```

Before the use of these data the cleaning from errors is a necessity. The maximum precipitation of 555  mm is obviously an error or a code. 

```{r save_data}
emy_data <- tibble::as.tibble(emy_data)
devtools::use_data(emy_data, overwrite = TRUE)

```

